### 2017-01-02 paper/evaluation.tex
pass on rq description

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}

\newcommand{\RQB}{\Fix{How often do developers use parallelism to improve
runtime performance?}}

\newcommand{\RQC}{What is the impact of parallalelization?}

@@

The first research question addresses the distribution of subjects per
time cost. We are interested in identifying time-consuming test suites
to investigate further their characteristics (\eg, type of application
and bottlenecks from execution).  The second research question
addresses our interest in understanding if developers are aware of
parallelism features from testing frameworks available out-of-the-box
through build systems (\eg, run JUnit test cases in parallel using
Maven Surefire) and what setting are often used. The third research
question addresses the impact of parallelism on the regression tests
from our sample set. We are interested in compare the execution
performance with different parallel settings (see
Section~\ref{sec:modes}). The fourth research question addresses the
characteristics of regression tests from the previous experiment.
More specifically, we want to investigate if there is a relation
between the balance of test execution (\ie, how uniformly distributed
is the execution time across tests cases) and the usage of
computational resources (\ie, if tests are mostly CPU or IO intense)
that impacts the effectiveness of parallelization. Finally, the fifth
research question discusses the limitations and insights to overcome
the pitfalls of parallelization.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we
run the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore them
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).

>>>>

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How often are parallelization features in build
files?}
\newcommand{\RQC}{What is the impact of parallalelization?}

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects.  The second research question
addresses our interest in understanding if developers are aware of
parallelization features from testing frameworks available
out-of-the-box through build systems (\eg, run JUnit test cases in
parallel using Maven Surefire) and what setting are more often used.
The third research question addresses the impact of parallelism on the
regression tests from our sample set. We are interested in compare the
execution performance with different parallel settings (see
Section~\ref{sec:modes}). The fourth research question addresses the
characteristics of regression tests from the previous experiment.
More specifically, we want to investigate if there is a relation
between the balance of test execution (\ie, how uniformly distributed
is the execution time across tests cases) and the usage of
computational resources (\ie, if tests are mostly CPU or IO intense)
that impacts the effectiveness of parallelization. Finally, the fifth
research question discusses the limitations and insights to overcome
the pitfalls of parallelization.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we run
the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore them
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).
We executed this experiment \Fix{X} times in our dedicated server
remotely via SSH with the operating system running only essential
services (\eg, the SSH server).
